---
title: 'Results for age-specific/mobility renewal model'
output:
  html_document: 
    default
params:
  stanModelFile:
    value: x
  job_dir:
    value: x
  states:
    value: x
  JOBID:
    value: x
---

```{r setup, include=FALSE}
library(knitr)
opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
args = params
file.to.figure = function(name) file.path(args$job_dir, 'figure',  paste0(args$stanModelFile, "-",args$JOBID, "-", name, ".png"))
file.to.table = function(name) file.path(args$job_dir, 'table', paste0(args$stanModelFile, "-",args$JOBID, "-", name, ".rds"))
```

## Session info
This file presents the results of Stan model 
```{r, echo=FALSE}
args$stanModelFile
```
with jobid
```{r, echo=FALSE}
args$JOBID
```

## Results

## Convergence diagnostics {.tabset .tabset-fade}

`r if ('AL' %in% args$states) '### Alabama'`

#### Effective sample size 
Listed below are the parameters with an effective sample size smaller than 500.

```{r, include=('AL' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_AL"))){
  neff <- readRDS(file.to.table("eff_sample_size_cum_AL"))
  neff[which(neff<500)]
}
```

#### Number of divergence and treedepth

```{r, include=('AL' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("diagnostics_AL"))){
  tmp <- readRDS(file.to.table("diagnostics_AL"))
  matrix(c('divergences', 'treedepth', tmp[[1]], tmp[[2]]), nrow = 2, ncol = 2, byrow = T)
}
```

#### WAIC
```{r, include=('AL' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("WAIC_AL"))){
  print(readRDS(file.to.table("WAIC_AL")))
}
```

#### LOO
```{r, include=('AL' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("LOO_AL"))){
  print(readRDS(file.to.table("LOO_AL")))
}
```

`r if ('AK' %in% args$states) '### Alaska'`

#### Effective sample size
Listed below are the parameters with an effective sample size smaller than 500.

```{r, include=('AK' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_AK"))){
  neff <- readRDS(file.to.table("eff_sample_size_cum_AK"))
  neff[which(neff<500)]
}
```

#### Number of divergence and treedepth

```{r, include=('AK' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("diagnostics_AK"))){
  tmp <- readRDS(file.to.table("diagnostics_AK"))
  matrix(c('divergences', 'treedepth', tmp[[1]], tmp[[2]]), nrow = 2, ncol = 2, byrow = T)
}
```

#### WAIC
```{r, include=('AK' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("WAIC_AK"))){
  print(readRDS(file.to.table("WAIC_AK")))
}
```

#### LOO
```{r, include=('AK' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("LOO_AK"))){
  print(readRDS(file.to.table("LOO_AK")))
}
```


`r if ('AZ' %in% args$states) '### Arizona'`

#### Effective sample size
Listed below are the parameters with an effective sample size smaller than 500.

```{r, include=('AZ' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_AZ"))){
  neff <- readRDS(file.to.table("eff_sample_size_cum_AZ"))
  neff[which(neff<500)]
}
```

#### Number of divergence and treedepth

```{r, include=('AZ' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("diagnostics_AZ"))){
  tmp <- readRDS(file.to.table("diagnostics_AZ"))
  matrix(c('divergences', 'treedepth', tmp[[1]], tmp[[2]]), nrow = 2, ncol = 2, byrow = T)
}
```

#### WAIC
```{r, include=('AZ' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("WAIC_AZ"))){
  print(readRDS(file.to.table("WAIC_AZ")))
}
```

#### LOO
```{r, include=('AZ' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("LOO_AZ"))){
  print(readRDS(file.to.table("LOO_AZ")))
}
```

`r if ('AR' %in% args$states) '### Arkansas'`

#### Effective sample size
Listed below are the parameters with an effective sample size smaller than 500.

```{r, include=('AR' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_AR"))){
  neff <- readRDS(file.to.table("eff_sample_size_cum_AR"))
  neff[which(neff<500)]
}
```

#### Number of divergence and treedepth

```{r, include=('AR' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("diagnostics_AR"))){
  tmp <- readRDS(file.to.table("diagnostics_AR"))
  matrix(c('divergences', 'treedepth', tmp[[1]], tmp[[2]]), nrow = 2, ncol = 2, byrow = T)
}
```

#### WAIC
```{r, include=('AR' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("WAIC_AR"))){
  print(readRDS(file.to.table("WAIC_AR")))
}
```

#### LOO
```{r, include=('AR' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("LOO_AR"))){
  print(readRDS(file.to.table("LOO_AR")))
}
```

`r if ('CA' %in% args$states) '### California'`

#### Effective sample size
Listed below are the parameters with an effective sample size smaller than 500.

```{r, include=('CA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_CA"))){
  neff <- readRDS(file.to.table("eff_sample_size_cum_CA"))
  neff[which(neff<500)]
}
```

#### Number of divergence and treedepth

```{r, include=('CA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("diagnostics_CA"))){
  tmp <- readRDS(file.to.table("diagnostics_CA"))
  matrix(c('divergences', 'treedepth', tmp[[1]], tmp[[2]]), nrow = 2, ncol = 2, byrow = T)
}
```

#### WAIC
```{r, include=('CA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("WAIC_CA"))){
  print(readRDS(file.to.table("WAIC_CA")))
}
```

#### LOO
```{r, include=('CA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("LOO_CA"))){
  print(readRDS(file.to.table("LOO_CA")))
}
```

`r if ('CO' %in% args$states) '### Colorado'`

#### Effective sample size
Listed below are the parameters with an effective sample size smaller than 500.

```{r, include=('CO' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_CO"))){
  neff <- readRDS(file.to.table("eff_sample_size_cum_CO"))
  neff[which(neff<500)]
}
```

#### Number of divergence and treedepth

```{r, include=('CO' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("diagnostics_CO"))){
  tmp <- readRDS(file.to.table("diagnostics_CO"))
  matrix(c('divergences', 'treedepth', tmp[[1]], tmp[[2]]), nrow = 2, ncol = 2, byrow = T)
}
```

#### Number of divergence and treedepth

```{r, include=('CO' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("diagnostics_CO"))){
  tmp <- readRDS(file.to.table("diagnostics_CO"))
  matrix(c('divergences', 'treedepth', tmp[[1]], tmp[[2]]), nrow = 2, ncol = 2, byrow = T)
}
```


#### WAIC
```{r, include=('CO' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("WAIC_CO"))){
  print(readRDS(file.to.table("WAIC_CO")))
}
```

#### LOO
```{r, include=('CO' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("LOO_CO"))){
  print(readRDS(file.to.table("LOO_CO")))
}
```

`r if ('CT' %in% args$states) '### Connecticut'`

#### Effective sample size
Listed below are the parameters with an effective sample size smaller than 500.

```{r, include=('CT' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_CT"))){
  neff <- readRDS(file.to.table("eff_sample_size_cum_CT"))
  neff[which(neff<500)]
}
```

#### Number of divergence and treedepth

```{r, include=('CT' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("diagnostics_CT"))){
  tmp <- readRDS(file.to.table("diagnostics_CT"))
  matrix(c('divergences', 'treedepth', tmp[[1]], tmp[[2]]), nrow = 2, ncol = 2, byrow = T)
}
```

#### WAIC
```{r, include=('CT' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("WAIC_CT"))){
  print(readRDS(file.to.table("WAIC_CT")))
}
```

#### LOO
```{r, include=('CT' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("LOO_CT"))){
  print(readRDS(file.to.table("LOO_CT")))
}
```

`r if ('DE' %in% args$states) '### Delaware'`

#### Effective sample size
Listed below are the parameters with an effective sample size smaller than 500.

```{r, include=('DE' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_DE"))){
  neff <- readRDS(file.to.table("eff_sample_size_cum_DE"))
  neff[which(neff<500)]
}
```

#### Number of divergence and treedepth

```{r, include=('DE' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("diagnostics_DE"))){
  tmp <- readRDS(file.to.table("diagnostics_DE"))
  matrix(c('divergences', 'treedepth', tmp[[1]], tmp[[2]]), nrow = 2, ncol = 2, byrow = T)
}
```

#### WAIC
```{r, include=('DE' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("WAIC_DE"))){
  print(readRDS(file.to.table("WAIC_DE")))
}
```

#### LOO
```{r, include=('DE' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("LOO_DE"))){
  print(readRDS(file.to.table("LOO_DE")))
}
```

`r if ('DC' %in% args$states) '### District of Columbia'`

#### Effective sample size
Listed below are the parameters with an effective sample size smaller than 500.

```{r, include=('DC' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_DC"))){
  neff <- readRDS(file.to.table("eff_sample_size_cum_DC"))
  neff[which(neff<500)]
}
```

#### Number of divergence and treedepth

```{r, include=('DC' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("diagnostics_DC"))){
  tmp <- readRDS(file.to.table("diagnostics_DC"))
  matrix(c('divergences', 'treedepth', tmp[[1]], tmp[[2]]), nrow = 2, ncol = 2, byrow = T)
}
```

#### WAIC
```{r, include=('DC' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("WAIC_DC"))){
  print(readRDS(file.to.table("WAIC_DC")))
}
```

#### LOO
```{r, include=('DC' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("LOO_DC"))){
  print(readRDS(file.to.table("LOO_DC")))
}
```

`r if ('FL' %in% args$states) '### Florida'`

#### Effective sample size
Listed below are the parameters with an effective sample size smaller than 500.

```{r, include=('FL' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_FL"))){
  neff <- readRDS(file.to.table("eff_sample_size_cum_FL"))
  neff[which(neff<500)]
}
```

#### Number of divergence and treedepth

```{r, include=('FL' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("diagnostics_FL"))){
  tmp <- readRDS(file.to.table("diagnostics_FL"))
  matrix(c('divergences', 'treedepth', tmp[[1]], tmp[[2]]), nrow = 2, ncol = 2, byrow = T)
}
```

#### WAIC
```{r, include=('FL' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("WAIC_FL"))){
  print(readRDS(file.to.table("WAIC_FL")))
}
```

#### LOO
```{r, include=('FL' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("LOO_FL"))){
  print(readRDS(file.to.table("LOO_FL")))
}
```

`r if ('GA' %in% args$states) '### Georgia'`

#### Effective sample size
Listed below are the parameters with an effective sample size smaller than 500.

```{r, include=('GA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_GA"))){
  neff <- readRDS(file.to.table("eff_sample_size_cum_GA"))
  neff[which(neff<500)]
}
```

#### Number of divergence and treedepth

```{r, include=('GA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("diagnostics_GA"))){
  tmp <- readRDS(file.to.table("diagnostics_GA"))
  matrix(c('divergences', 'treedepth', tmp[[1]], tmp[[2]]), nrow = 2, ncol = 2, byrow = T)
}
```

#### WAIC
```{r, include=('GA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("WAIC_GA"))){
  print(readRDS(file.to.table("WAIC_GA")))
}
```

#### LOO
```{r, include=('GA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("LOO_GA"))){
  print(readRDS(file.to.table("LOO_GA")))
}
```

`r if ('HI' %in% args$states) '### Hawaii'`

#### Effective sample size
Listed below are the parameters with an effective sample size smaller than 500.

```{r, include=('HI' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_HI"))){
  neff <- readRDS(file.to.table("eff_sample_size_cum_HI"))
  neff[which(neff<500)]
}
```

#### Number of divergence and treedepth

```{r, include=('HI' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("diagnostics_HI"))){
  tmp <- readRDS(file.to.table("diagnostics_HI"))
  matrix(c('divergences', 'treedepth', tmp[[1]], tmp[[2]]), nrow = 2, ncol = 2, byrow = T)
}
```

#### WAIC
```{r, include=('HI' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("WAIC_HI"))){
  print(readRDS(file.to.table("WAIC_HI")))
}
```

#### LOO
```{r, include=('HI' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("LOO_HI"))){
  print(readRDS(file.to.table("LOO_HI")))
}
```

`r if ('ID' %in% args$states) '### Indiana'`

#### Effective sample size
Listed below are the parameters with an effective sample size smaller than 500.

```{r, include=('ID' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_ID"))){
  neff <- readRDS(file.to.table("eff_sample_size_cum_ID"))
  neff[which(neff<500)]
}
```

#### Number of divergence and treedepth

```{r, include=('ID' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("diagnostics_ID"))){
  tmp <- readRDS(file.to.table("diagnostics_ID"))
  matrix(c('divergences', 'treedepth', tmp[[1]], tmp[[2]]), nrow = 2, ncol = 2, byrow = T)
}
```

#### WAIC
```{r, include=('ID' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("WAIC_ID"))){
  print(readRDS(file.to.table("WAIC_ID")))
}
```

#### LOO
```{r, include=('ID' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("LOO_ID"))){
  print(readRDS(file.to.table("LOO_ID")))
}
```

`r if ('IL' %in% args$states) '### Illinois'`

#### Effective sample size
Listed below are the parameters with an effective sample size smaller than 500.

```{r, include=('IL' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_IL"))){
  neff <- readRDS(file.to.table("eff_sample_size_cum_IL"))
  neff[which(neff<500)]
}
```

#### Number of divergence and treedepth

```{r, include=('IL' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("diagnostics_IL"))){
  tmp <- readRDS(file.to.table("diagnostics_IL"))
  matrix(c('divergences', 'treedepth', tmp[[1]], tmp[[2]]), nrow = 2, ncol = 2, byrow = T)
}
```

#### WAIC
```{r, include=('IL' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("WAIC_IL"))){
  print(readRDS(file.to.table("WAIC_IL")))
}
```

#### LOO
```{r, include=('IL' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("LOO_IL"))){
  print(readRDS(file.to.table("LOO_IL")))
}
```

`r if ('ID' %in% args$states) '### Idaho'`

#### Effective sample size
Listed below are the parameters with an effective sample size smaller than 500.

```{r, include=('ID' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_ID"))){
  neff <- readRDS(file.to.table("eff_sample_size_cum_ID"))
  neff[which(neff<500)]
}
```

#### Number of divergence and treedepth

```{r, include=('ID' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("diagnostics_ID"))){
  tmp <- readRDS(file.to.table("diagnostics_ID"))
  matrix(c('divergences', 'treedepth', tmp[[1]], tmp[[2]]), nrow = 2, ncol = 2, byrow = T)
}
```

#### WAIC
```{r, include=('ID' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("WAIC_ID"))){
  print(readRDS(file.to.table("WAIC_ID")))
}
```

#### LOO
```{r, include=('ID' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("LOO_ID"))){
  print(readRDS(file.to.table("LOO_ID")))
}
```


`r if ('IN' %in% args$states) '### Indiana'`

#### Effective sample size
Listed below are the parameters with an effective sample size smaller than 500.

```{r, include=('IN' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_IN"))){
  neff <- readRDS(file.to.table("eff_sample_size_cum_IN"))
  neff[which(neff<500)]
}
```

#### Number of divergence and treedepth

```{r, include=('IN' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("diagnostics_IN"))){
  tmp <- readRDS(file.to.table("diagnostics_IN"))
  matrix(c('divergences', 'treedepth', tmp[[1]], tmp[[2]]), nrow = 2, ncol = 2, byrow = T)
}
```

#### WAIC
```{r, include=('IN' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("WAIC_IN"))){
  print(readRDS(file.to.table("WAIC_IN")))
}
```

#### LOO
```{r, include=('IN' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("LOO_IN"))){
  print(readRDS(file.to.table("LOO_IN")))
}
```

`r if ('IA' %in% args$states) '### Iowa'`

#### Effective sample size
Listed below are the parameters with an effective sample size smaller than 500.

```{r, include=('IA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_IA"))){
  neff <- readRDS(file.to.table("eff_sample_size_cum_IA"))
  neff[which(neff<500)]
}
```

#### Number of divergence and treedepth

```{r, include=('IA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("diagnostics_IA"))){
  tmp <- readRDS(file.to.table("diagnostics_IA"))
  matrix(c('divergences', 'treedepth', tmp[[1]], tmp[[2]]), nrow = 2, ncol = 2, byrow = T)
}
```

#### WAIC
```{r, include=('IA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("WAIC_IA"))){
  print(readRDS(file.to.table("WAIC_IA")))
}
```

#### LOO
```{r, include=('IA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("LOO_IA"))){
  print(readRDS(file.to.table("LOO_IA")))
}
```

`r if ('KS' %in% args$states) '### Kansas'`

#### Effective sample size
Listed below are the parameters with an effective sample size smaller than 500.

```{r, include=('KS' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_KS"))){
  neff <- readRDS(file.to.table("eff_sample_size_cum_KS"))
  neff[which(neff<500)]
}
```

#### Number of divergence and treedepth

```{r, include=('KS' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("diagnostics_KS"))){
  tmp <- readRDS(file.to.table("diagnostics_KS"))
  matrix(c('divergences', 'treedepth', tmp[[1]], tmp[[2]]), nrow = 2, ncol = 2, byrow = T)
}
```

#### WAIC
```{r, include=('KS' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("WAIC_KS"))){
  print(readRDS(file.to.table("WAIC_KS")))
}
```

#### LOO
```{r, include=('KS' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("LOO_KS"))){
  print(readRDS(file.to.table("LOO_KS")))
}
```

`r if ('KY' %in% args$states) '### Kentucky'`

#### Effective sample size
Listed below are the parameters with an effective sample size smaller than 500.

```{r, include=('KY' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_KY"))){
  neff <- readRDS(file.to.table("eff_sample_size_cum_KY"))
  neff[which(neff<500)]
}
```

#### Number of divergence and treedepth

```{r, include=('KY' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("diagnostics_KY"))){
  tmp <- readRDS(file.to.table("diagnostics_KY"))
  matrix(c('divergences', 'treedepth', tmp[[1]], tmp[[2]]), nrow = 2, ncol = 2, byrow = T)
}
```

#### WAIC
```{r, include=('KY' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("WAIC_KY"))){
  print(readRDS(file.to.table("WAIC_KY")))
}
```

#### LOO
```{r, include=('KY' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("LOO_KY"))){
  print(readRDS(file.to.table("LOO_KY")))
}
```

`r if ('LA' %in% args$states) '### Louisiana'`

#### Effective sample size
Listed below are the parameters with an effective sample size smaller than 500.

```{r, include=('LA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_LA"))){
  neff <- readRDS(file.to.table("eff_sample_size_cum_LA"))
  neff[which(neff<500)]
}
```

#### Number of divergence and treedepth

```{r, include=('LA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("diagnostics_LA"))){
  tmp <- readRDS(file.to.table("diagnostics_LA"))
  matrix(c('divergences', 'treedepth', tmp[[1]], tmp[[2]]), nrow = 2, ncol = 2, byrow = T)
}
```

#### WAIC
```{r, include=('LA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("WAIC_LA"))){
  print(readRDS(file.to.table("WAIC_LA")))
}
```

#### LOO
```{r, include=('LA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("LOO_LA"))){
  print(readRDS(file.to.table("LOO_LA")))
}
```

`r if ('ME' %in% args$states) '### Maine'`

#### Effective sample size
Listed below are the parameters with an effective sample size smaller than 500.

```{r, include=('ME' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_ME"))){
  neff <- readRDS(file.to.table("eff_sample_size_cum_ME"))
  neff[which(neff<500)]
}
```

#### Number of divergence and treedepth

```{r, include=('ME' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("diagnostics_ME"))){
  tmp <- readRDS(file.to.table("diagnostics_ME"))
  matrix(c('divergences', 'treedepth', tmp[[1]], tmp[[2]]), nrow = 2, ncol = 2, byrow = T)
}
```

#### WAIC
```{r, include=('ME' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("WAIC_ME"))){
  print(readRDS(file.to.table("WAIC_ME")))
}
```

#### LOO
```{r, include=('ME' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("LOO_ME"))){
  print(readRDS(file.to.table("LOO_ME")))
}
```

`r if ('MD' %in% args$states) '### Maryland'`

#### Effective sample size
Listed below are the parameters with an effective sample size smaller than 500.

```{r, include=('MD' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_MD"))){
  neff <- readRDS(file.to.table("eff_sample_size_cum_MD"))
  neff[which(neff<500)]
}
```

#### Number of divergence and treedepth

```{r, include=('MD' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("diagnostics_MD"))){
  tmp <- readRDS(file.to.table("diagnostics_MD"))
  matrix(c('divergences', 'treedepth', tmp[[1]], tmp[[2]]), nrow = 2, ncol = 2, byrow = T)
}
```

#### WAIC
```{r, include=('MD' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("WAIC_MD"))){
  print(readRDS(file.to.table("WAIC_MD")))
}
```

#### LOO
```{r, include=('MD' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("LOO_MD"))){
  print(readRDS(file.to.table("LOO_MD")))
}
```

`r if ('MA' %in% args$states) '### Massachusetts'`

#### Effective sample size
Listed below are the parameters with an effective sample size smaller than 500.

```{r, include=('MA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_MA"))){
  neff <- readRDS(file.to.table("eff_sample_size_cum_MA"))
  neff[which(neff<500)]
}
```

#### Number of divergence and treedepth

```{r, include=('MA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("diagnostics_MA"))){
  tmp <- readRDS(file.to.table("diagnostics_MA"))
  matrix(c('divergences', 'treedepth', tmp[[1]], tmp[[2]]), nrow = 2, ncol = 2, byrow = T)
}
```

#### WAIC
```{r, include=('MA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("WAIC_MA"))){
  print(readRDS(file.to.table("WAIC_MA")))
}
```

#### LOO
```{r, include=('MA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("LOO_MA"))){
  print(readRDS(file.to.table("LOO_MA")))
}
```

`r if ('MI' %in% args$states) '### Michigan'`

#### Effective sample size
Listed below are the parameters with an effective sample size smaller than 500.

```{r, include=('MI' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_MI"))){
  neff <- readRDS(file.to.table("eff_sample_size_cum_MI"))
  neff[which(neff<500)]
}
```

#### Number of divergence and treedepth

```{r, include=('MI' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("diagnostics_MI"))){
  tmp <- readRDS(file.to.table("diagnostics_MI"))
  matrix(c('divergences', 'treedepth', tmp[[1]], tmp[[2]]), nrow = 2, ncol = 2, byrow = T)
}
```

#### WAIC
```{r, include=('MI' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("WAIC_MI"))){
  print(readRDS(file.to.table("WAIC_MI")))
}
```

#### LOO
```{r, include=('MI' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("LOO_MI"))){
  print(readRDS(file.to.table("LOO_MI")))
}
```

`r if ('MN' %in% args$states) '### Minnesota'`

#### Effective sample size
Listed below are the parameters with an effective sample size smaller than 500.

```{r, include=('MN' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_MN"))){
  neff <- readRDS(file.to.table("eff_sample_size_cum_MN"))
  neff[which(neff<500)]
}
```

#### Number of divergence and treedepth

```{r, include=('MN' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("diagnostics_MN"))){
  tmp <- readRDS(file.to.table("diagnostics_MN"))
  matrix(c('divergences', 'treedepth', tmp[[1]], tmp[[2]]), nrow = 2, ncol = 2, byrow = T)
}
```

#### WAIC
```{r, include=('MN' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("WAIC_MN"))){
  print(readRDS(file.to.table("WAIC_MN")))
}
```

#### LOO
```{r, include=('MN' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("LOO_MN"))){
  print(readRDS(file.to.table("LOO_MN")))
}
```

`r if ('MS' %in% args$states) '### Mississippi'`

#### Effective sample size
Listed below are the parameters with an effective sample size smaller than 500.

```{r, include=('MS' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_MS"))){
  neff <- readRDS(file.to.table("eff_sample_size_cum_MS"))
  neff[which(neff<500)]
}
```

#### Number of divergence and treedepth

```{r, include=('MS' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("diagnostics_MS"))){
  tmp <- readRDS(file.to.table("diagnostics_MS"))
  matrix(c('divergences', 'treedepth', tmp[[1]], tmp[[2]]), nrow = 2, ncol = 2, byrow = T)
}
```

#### WAIC
```{r, include=('MS' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("WAIC_MS"))){
  print(readRDS(file.to.table("WAIC_MS")))
}
```

#### LOO
```{r, include=('MS' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("LOO_MS"))){
  print(readRDS(file.to.table("LOO_MS")))
}
```

`r if ('MO' %in% args$states) '### Missouri'`

#### Effective sample size
Listed below are the parameters with an effective sample size smaller than 500.

```{r, include=('MO' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_MO"))){
  neff <- readRDS(file.to.table("eff_sample_size_cum_MO"))
  neff[which(neff<500)]
}
```

#### Number of divergence and treedepth

```{r, include=('MO' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("diagnostics_MO"))){
  tmp <- readRDS(file.to.table("diagnostics_MO"))
  matrix(c('divergences', 'treedepth', tmp[[1]], tmp[[2]]), nrow = 2, ncol = 2, byrow = T)
}
```

#### WAIC
```{r, include=('MO' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("WAIC_MO"))){
  print(readRDS(file.to.table("WAIC_MO")))
}
```

#### LOO
```{r, include=('MO' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("LOO_MO"))){
  print(readRDS(file.to.table("LOO_MO")))
}
```

`r if ('MT' %in% args$states) '### Montana'`

#### Effective sample size
Listed below are the parameters with an effective sample size smaller than 500.

```{r, include=('MT' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_MT"))){
  neff <- readRDS(file.to.table("eff_sample_size_cum_MT"))
  neff[which(neff<500)]
}
```

#### Number of divergence and treedepth

```{r, include=('MT' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("diagnostics_MT"))){
  tmp <- readRDS(file.to.table("diagnostics_MT"))
  matrix(c('divergences', 'treedepth', tmp[[1]], tmp[[2]]), nrow = 2, ncol = 2, byrow = T)
}
```

#### WAIC
```{r, include=('MT' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("WAIC_MT"))){
  print(readRDS(file.to.table("WAIC_MT")))
}
```

#### LOO
```{r, include=('MT' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("LOO_MT"))){
  print(readRDS(file.to.table("LOO_MT")))
}
```

`r if ('NE' %in% args$states) '### Nebraska'`

#### Effective sample size
Listed below are the parameters with an effective sample size smaller than 500.

```{r, include=('NE' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_NE"))){
  neff <- readRDS(file.to.table("eff_sample_size_cum_NE"))
  neff[which(neff<500)]
}
```

#### Number of divergence and treedepth

```{r, include=('NE' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("diagnostics_NE"))){
  tmp <- readRDS(file.to.table("diagnostics_NE"))
  matrix(c('divergences', 'treedepth', tmp[[1]], tmp[[2]]), nrow = 2, ncol = 2, byrow = T)
}
```

#### WAIC
```{r, include=('NE' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("WAIC_NE"))){
  print(readRDS(file.to.table("WAIC_NE")))
}
```

#### LOO
```{r, include=('NE' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("LOO_NE"))){
  print(readRDS(file.to.table("LOO_NE")))
}
```

`r if ('NV' %in% args$states) '### Nevada'`

#### Effective sample size
Listed below are the parameters with an effective sample size smaller than 500.

```{r, include=('NV' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_NV"))){
  neff <- readRDS(file.to.table("eff_sample_size_cum_NV"))
  neff[which(neff<500)]
}
```

#### Number of divergence and treedepth

```{r, include=('NV' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("diagnostics_NV"))){
  tmp <- readRDS(file.to.table("diagnostics_NV"))
  matrix(c('divergences', 'treedepth', tmp[[1]], tmp[[2]]), nrow = 2, ncol = 2, byrow = T)
}
```

#### WAIC
```{r, include=('NV' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("WAIC_NV"))){
  print(readRDS(file.to.table("WAIC_NV")))
}
```

#### LOO
```{r, include=('NV' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("LOO_NV"))){
  print(readRDS(file.to.table("LOO_NV")))
}
```

`r if ('NH' %in% args$states) '### New Hampshire'`

#### Effective sample size
Listed below are the parameters with an effective sample size smaller than 500.

```{r, include=('NH' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_NH"))){
  neff <- readRDS(file.to.table("eff_sample_size_cum_NH"))
  neff[which(neff<500)]
}
```

#### Number of divergence and treedepth

```{r, include=('NH' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("diagnostics_NH"))){
  tmp <- readRDS(file.to.table("diagnostics_NH"))
  matrix(c('divergences', 'treedepth', tmp[[1]], tmp[[2]]), nrow = 2, ncol = 2, byrow = T)
}
```

#### WAIC
```{r, include=('NH' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("WAIC_NH"))){
  print(readRDS(file.to.table("WAIC_NH")))
}
```

#### LOO
```{r, include=('NH' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("LOO_NH"))){
  print(readRDS(file.to.table("LOO_NH")))
}
```

`r if ('NJ' %in% args$states) '### New Jersey'`

#### Effective sample size
Listed below are the parameters with an effective sample size smaller than 500.

```{r, include=('NJ' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_NJ"))){
  neff <- readRDS(file.to.table("eff_sample_size_cum_NJ"))
  neff[which(neff<500)]
}
```

#### Number of divergence and treedepth

```{r, include=('NJ' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("diagnostics_NJ"))){
  tmp <- readRDS(file.to.table("diagnostics_NJ"))
  matrix(c('divergences', 'treedepth', tmp[[1]], tmp[[2]]), nrow = 2, ncol = 2, byrow = T)
}
```

#### WAIC
```{r, include=('NJ' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("WAIC_NJ"))){
  print(readRDS(file.to.table("WAIC_NJ")))
}
```

#### LOO
```{r, include=('NJ' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("LOO_NJ"))){
  print(readRDS(file.to.table("LOO_NJ")))
}
```

`r if ('NM' %in% args$states) '### New Mexico'`

#### Effective sample size
Listed below are the parameters with an effective sample size smaller than 500.

```{r, include=('NM' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_NM"))){
  neff <- readRDS(file.to.table("eff_sample_size_cum_NM"))
  neff[which(neff<500)]
}
```

#### Number of divergence and treedepth

```{r, include=('NM' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("diagnostics_NM"))){
  tmp <- readRDS(file.to.table("diagnostics_NM"))
  matrix(c('divergences', 'treedepth', tmp[[1]], tmp[[2]]), nrow = 2, ncol = 2, byrow = T)
}
```

#### WAIC
```{r, include=('NM' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("WAIC_NM"))){
  print(readRDS(file.to.table("WAIC_NM")))
}
```

#### LOO
```{r, include=('NM' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("LOO_NM"))){
  print(readRDS(file.to.table("LOO_NM")))
}
```

`r if ('NY' %in% args$states) '### New York'`

#### Effective sample size
Listed below are the parameters with an effective sample size smaller than 500.

```{r, include=('NY' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_NY"))){
  neff <- readRDS(file.to.table("eff_sample_size_cum_NY"))
  neff[which(neff<500)]
}
```

#### Number of divergence and treedepth

```{r, include=('NY' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("diagnostics_NY"))){
  tmp <- readRDS(file.to.table("diagnostics_NY"))
  matrix(c('divergences', 'treedepth', tmp[[1]], tmp[[2]]), nrow = 2, ncol = 2, byrow = T)
}
```

#### WAIC
```{r, include=('NY' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("WAIC_NY"))){
  print(readRDS(file.to.table("WAIC_NY")))
}
```

#### LOO
```{r, include=('NY' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("LOO_NY"))){
  print(readRDS(file.to.table("LOO_NY")))
}
```

`r if ('NYC' %in% args$states) '### New York City'`

#### Effective sample size
Listed below are the parameters with an effective sample size smaller than 500.

```{r, include=('NYC' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_NYC"))){
  neff <- readRDS(file.to.table("eff_sample_size_cum_NYC"))
  neff[which(neff<500)]
}
```

#### Number of divergence and treedepth

```{r, include=('NYC' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("diagnostics_NYC"))){
  tmp <- readRDS(file.to.table("diagnostics_NYC"))
  matrix(c('divergences', 'treedepth', tmp[[1]], tmp[[2]]), nrow = 2, ncol = 2, byrow = T)
}
```

#### WAIC
```{r, include=('NYC' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("WAIC_NYC"))){
  print(readRDS(file.to.table("WAIC_NYC")))
}
```

#### LOO
```{r, include=('NYC' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("LOO_NYC"))){
  print(readRDS(file.to.table("LOO_NYC")))
}
```

`r if ('NC' %in% args$states) '### North Carolina'`

#### Effective sample size
Listed below are the parameters with an effective sample size smaller than 500.

```{r, include=('NC' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_NC"))){
  neff <- readRDS(file.to.table("eff_sample_size_cum_NC"))
  neff[which(neff<500)]
}
```

#### Number of divergence and treedepth

```{r, include=('NC' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("diagnostics_NC"))){
  tmp <- readRDS(file.to.table("diagnostics_NC"))
  matrix(c('divergences', 'treedepth', tmp[[1]], tmp[[2]]), nrow = 2, ncol = 2, byrow = T)
}
```

#### WAIC
```{r, include=('NC' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("WAIC_NC"))){
  print(readRDS(file.to.table("WAIC_NC")))
}
```

#### LOO
```{r, include=('NC' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("LOO_NC"))){
  print(readRDS(file.to.table("LOO_NC")))
}
```

`r if ('ND' %in% args$states) '### North Dakota'`

#### Effective sample size
Listed below are the parameters with an effective sample size smaller than 500.

```{r, include=('ND' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_ND"))){
  neff <- readRDS(file.to.table("eff_sample_size_cum_ND"))
  neff[which(neff<500)]
}
```

#### Number of divergence and treedepth

```{r, include=('ND' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("diagnostics_ND"))){
  tmp <- readRDS(file.to.table("diagnostics_ND"))
  matrix(c('divergences', 'treedepth', tmp[[1]], tmp[[2]]), nrow = 2, ncol = 2, byrow = T)
}
```

#### WAIC
```{r, include=('ND' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("WAIC_ND"))){
  print(readRDS(file.to.table("WAIC_ND")))
}
```

#### LOO
```{r, include=('ND' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("LOO_ND"))){
  print(readRDS(file.to.table("LOO_ND")))
}
```

`r if ('OH' %in% args$states) '### Ohio'`

#### Effective sample size
Listed below are the parameters with an effective sample size smaller than 500.

```{r, include=('OH' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_OH"))){
  neff <- readRDS(file.to.table("eff_sample_size_cum_OH"))
  neff[which(neff<500)]
}
```

#### Number of divergence and treedepth

```{r, include=('OH' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("diagnostics_OH"))){
  tmp <- readRDS(file.to.table("diagnostics_OH"))
  matrix(c('divergences', 'treedepth', tmp[[1]], tmp[[2]]), nrow = 2, ncol = 2, byrow = T)
}
```

#### WAIC
```{r, include=('OH' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("WAIC_OH"))){
  print(readRDS(file.to.table("WAIC_OH")))
}
```

#### LOO
```{r, include=('OH' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("LOO_OH"))){
  print(readRDS(file.to.table("LOO_OH")))
}
```

`r if ('OK' %in% args$states) '### Oklahoma'`

#### Effective sample size
Listed below are the parameters with an effective sample size smaller than 500.

```{r, include=('OK' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_OK"))){
  neff <- readRDS(file.to.table("eff_sample_size_cum_OK"))
  neff[which(neff<500)]
}
```

#### Number of divergence and treedepth

```{r, include=('OK' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("diagnostics_OK"))){
  tmp <- readRDS(file.to.table("diagnostics_OK"))
  matrix(c('divergences', 'treedepth', tmp[[1]], tmp[[2]]), nrow = 2, ncol = 2, byrow = T)
}
```

#### WAIC
```{r, include=('OK' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("WAIC_OK"))){
  print(readRDS(file.to.table("WAIC_OK")))
}
```

#### LOO
```{r, include=('OK' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("LOO_OK"))){
  print(readRDS(file.to.table("LOO_OK")))
}
```

`r if ('OR' %in% args$states) '### Oregon'`

#### Effective sample size
Listed below are the parameters with an effective sample size smaller than 500.

```{r, include=('OR' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_OR"))){
  neff <- readRDS(file.to.table("eff_sample_size_cum_OR"))
  neff[which(neff<500)]
}
```

#### Number of divergence and treedepth

```{r, include=('OR' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("diagnostics_OR"))){
  tmp <- readRDS(file.to.table("diagnostics_OR"))
  matrix(c('divergences', 'treedepth', tmp[[1]], tmp[[2]]), nrow = 2, ncol = 2, byrow = T)
}
```

#### WAIC
```{r, include=('OR' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("WAIC_OR"))){
  print(readRDS(file.to.table("WAIC_OR")))
}
```

#### LOO
```{r, include=('OR' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("LOO_OR"))){
  print(readRDS(file.to.table("LOO_OR")))
}
```


`r if ('PA' %in% args$states) '### Pennsylvania'`

#### Effective sample size
Listed below are the parameters with an effective sample size smaller than 500.

```{r, include=('PA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_PA"))){
  neff <- readRDS(file.to.table("eff_sample_size_cum_PA"))
  neff[which(neff<500)]
}
```

#### Number of divergence and treedepth

```{r, include=('PA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("diagnostics_PA"))){
  tmp <- readRDS(file.to.table("diagnostics_PA"))
  matrix(c('divergences', 'treedepth', tmp[[1]], tmp[[2]]), nrow = 2, ncol = 2, byrow = T)
}
```

#### WAIC
```{r, include=('PA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("WAIC_PA"))){
  print(readRDS(file.to.table("WAIC_PA")))
}
```

#### LOO
```{r, include=('PA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("LOO_PA"))){
  print(readRDS(file.to.table("LOO_PA")))
}
```

`r if ('RI' %in% args$states) '### Rhode Island'`

#### Effective sample size
Listed below are the parameters with an effective sample size smaller than 500.

```{r, include=('RI' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_RI"))){
  neff <- readRDS(file.to.table("eff_sample_size_cum_RI"))
  neff[which(neff<500)]
}
```

#### Number of divergence and treedepth

```{r, include=('RI' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("diagnostics_RI"))){
  tmp <- readRDS(file.to.table("diagnostics_RI"))
  matrix(c('divergences', 'treedepth', tmp[[1]], tmp[[2]]), nrow = 2, ncol = 2, byrow = T)
}
```

#### WAIC
```{r, include=('RI' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("WAIC_RI"))){
  print(readRDS(file.to.table("WAIC_RI")))
}
```

#### LOO
```{r, include=('RI' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("LOO_RI"))){
  print(readRDS(file.to.table("LOO_RI")))
}
```

`r if ('SC' %in% args$states) '### South Carolina'`

#### Effective sample size
Listed below are the parameters with an effective sample size smaller than 500.

```{r, include=('SC' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_SC"))){
  neff <- readRDS(file.to.table("eff_sample_size_cum_SC"))
  neff[which(neff<500)]
}
```

#### Number of divergence and treedepth

```{r, include=('SC' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("diagnostics_SC"))){
  tmp <- readRDS(file.to.table("diagnostics_SC"))
  matrix(c('divergences', 'treedepth', tmp[[1]], tmp[[2]]), nrow = 2, ncol = 2, byrow = T)
}
```

#### WAIC
```{r, include=('SC' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("WAIC_SC"))){
  print(readRDS(file.to.table("WAIC_SC")))
}
```

#### LOO
```{r, include=('SC' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("LOO_SC"))){
  print(readRDS(file.to.table("LOO_SC")))
}
```

`r if ('SD' %in% args$states) '### South Dakota'`

#### Effective sample size
Listed below are the parameters with an effective sample size smaller than 500.

```{r, include=('SD' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_SD"))){
  neff <- readRDS(file.to.table("eff_sample_size_cum_SD"))
  neff[which(neff<500)]
}
```

#### Number of divergence and treedepth

```{r, include=('SD' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("diagnostics_SD"))){
  tmp <- readRDS(file.to.table("diagnostics_SD"))
  matrix(c('divergences', 'treedepth', tmp[[1]], tmp[[2]]), nrow = 2, ncol = 2, byrow = T)
}
```

#### WAIC
```{r, include=('SD' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("WAIC_SD"))){
  print(readRDS(file.to.table("WAIC_SD")))
}
```

#### LOO
```{r, include=('SD' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("LOO_SD"))){
  print(readRDS(file.to.table("LOO_SD")))
}
```

`r if ('TN' %in% args$states) '### Tennessee'`

#### Effective sample size
Listed below are the parameters with an effective sample size smaller than 500.

```{r, include=('TN' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_TN"))){
  neff <- readRDS(file.to.table("eff_sample_size_cum_TN"))
  neff[which(neff<500)]
}
```

#### Number of divergence and treedepth

```{r, include=('TN' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("diagnostics_TN"))){
  tmp <- readRDS(file.to.table("diagnostics_TN"))
  matrix(c('divergences', 'treedepth', tmp[[1]], tmp[[2]]), nrow = 2, ncol = 2, byrow = T)
}
```

#### WAIC
```{r, include=('TN' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("WAIC_TN"))){
  print(readRDS(file.to.table("WAIC_TN")))
}
```

#### LOO
```{r, include=('TN' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("LOO_TN"))){
  print(readRDS(file.to.table("LOO_TN")))
}
```

`r if ('TX' %in% args$states) '### Texas'`

#### Effective sample size
Listed below are the parameters with an effective sample size smaller than 500.

```{r, include=('TX' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_TX"))){
  neff <- readRDS(file.to.table("eff_sample_size_cum_TX"))
  neff[which(neff<500)]
}
```

#### Number of divergence and treedepth

```{r, include=('TX' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("diagnostics_TX"))){
  tmp <- readRDS(file.to.table("diagnostics_TX"))
  matrix(c('divergences', 'treedepth', tmp[[1]], tmp[[2]]), nrow = 2, ncol = 2, byrow = T)
}
```

#### WAIC
```{r, include=('TX' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("WAIC_TX"))){
  print(readRDS(file.to.table("WAIC_TX")))
}
```

#### LOO
```{r, include=('TX' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("LOO_TX"))){
  print(readRDS(file.to.table("LOO_TX")))
}
```

`r if ('UT' %in% args$states) '### Utah'`

#### Effective sample size
Listed below are the parameters with an effective sample size smaller than 500.

```{r, include=('UT' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_UT"))){
  neff <- readRDS(file.to.table("eff_sample_size_cum_UT"))
  neff[which(neff<500)]
}
```

#### Number of divergence and treedepth

```{r, include=('UT' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("diagnostics_UT"))){
  tmp <- readRDS(file.to.table("diagnostics_UT"))
  matrix(c('divergences', 'treedepth', tmp[[1]], tmp[[2]]), nrow = 2, ncol = 2, byrow = T)
}
```

#### WAIC
```{r, include=('UT' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("WAIC_UT"))){
  print(readRDS(file.to.table("WAIC_UT")))
}
```

#### LOO
```{r, include=('UT' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("LOO_UT"))){
  print(readRDS(file.to.table("LOO_UT")))
}
```

`r if ('VT' %in% args$states) '### Vermont'`

#### Effective sample size
Listed below are the parameters with an effective sample size smaller than 500.

```{r, include=('VT' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_VT"))){
  neff <- readRDS(file.to.table("eff_sample_size_cum_VT"))
  neff[which(neff<500)]
}
```

#### Number of divergence and treedepth

```{r, include=('VT' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("diagnostics_VT"))){
  tmp <- readRDS(file.to.table("diagnostics_VT"))
  matrix(c('divergences', 'treedepth', tmp[[1]], tmp[[2]]), nrow = 2, ncol = 2, byrow = T)
}
```

#### WAIC
```{r, include=('VT' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("WAIC_VT"))){
  print(readRDS(file.to.table("WAIC_VT")))
}
```

#### LOO
```{r, include=('VT' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("LOO_VT"))){
  print(readRDS(file.to.table("LOO_VT")))
}
```

`r if ('VA' %in% args$states) '### Virginia'`

#### Effective sample size
Listed below are the parameters with an effective sample size smaller than 500.

```{r, include=('VA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_VA"))){
  neff <- readRDS(file.to.table("eff_sample_size_cum_VA"))
  neff[which(neff<500)]
}
```

#### Number of divergence and treedepth

```{r, include=('VA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("diagnostics_VA"))){
  tmp <- readRDS(file.to.table("diagnostics_VA"))
  matrix(c('divergences', 'treedepth', tmp[[1]], tmp[[2]]), nrow = 2, ncol = 2, byrow = T)
}
```

#### WAIC
```{r, include=('VA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("WAIC_VA"))){
  print(readRDS(file.to.table("WAIC_VA")))
}
```

#### LOO
```{r, include=('VA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("LOO_VA"))){
  print(readRDS(file.to.table("LOO_VA")))
}
```

`r if ('WA' %in% args$states) '### Washington'`

#### Effective sample size
Listed below are the parameters with an effective sample size smaller than 500.

```{r, include=('WA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_WA"))){
  neff <- readRDS(file.to.table("eff_sample_size_cum_WA"))
  neff[which(neff<500)]
}
```

#### Number of divergence and treedepth

```{r, include=('WA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("diagnostics_WA"))){
  tmp <- readRDS(file.to.table("diagnostics_WA"))
  matrix(c('divergences', 'treedepth', tmp[[1]], tmp[[2]]), nrow = 2, ncol = 2, byrow = T)
}
```

#### WAIC
```{r, include=('WA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("WAIC_WA"))){
  print(readRDS(file.to.table("WAIC_WA")))
}
```

#### LOO
```{r, include=('WA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("LOO_WA"))){
  print(readRDS(file.to.table("LOO_WA")))
}
```

`r if ('WV' %in% args$states) '### West Virginia'`

#### Effective sample size
Listed below are the parameters with an effective sample size smaller than 500.

```{r, include=('WV' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_WV"))){
  neff <- readRDS(file.to.table("eff_sample_size_cum_WV"))
  neff[which(neff<500)]
}
```

#### Number of divergence and treedepth

```{r, include=('WV' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("diagnostics_WV"))){
  tmp <- readRDS(file.to.table("diagnostics_WV"))
  matrix(c('divergences', 'treedepth', tmp[[1]], tmp[[2]]), nrow = 2, ncol = 2, byrow = T)
}
```

#### WAIC
```{r, include=('WV' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("WAIC_WV"))){
  print(readRDS(file.to.table("WAIC_WV")))
}
```

#### LOO
```{r, include=('WV' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("LOO_WV"))){
  print(readRDS(file.to.table("LOO_WV")))
}
```

`r if ('WI' %in% args$states) '### Wisconsin'`

#### Effective sample size
Listed below are the parameters with an effective sample size smaller than 500.

```{r, include=('WI' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_WI"))){
  neff <- readRDS(file.to.table("eff_sample_size_cum_WI"))
  neff[which(neff<500)]
}
```

#### Number of divergence and treedepth

```{r, include=('WI' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("diagnostics_WI"))){
  tmp <- readRDS(file.to.table("diagnostics_WI"))
  matrix(c('divergences', 'treedepth', tmp[[1]], tmp[[2]]), nrow = 2, ncol = 2, byrow = T)
}
```

#### WAIC
```{r, include=('WI' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("WAIC_WI"))){
  print(readRDS(file.to.table("WAIC_WI")))
}
```

#### LOO
```{r, include=('WI' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("LOO_WI"))){
  print(readRDS(file.to.table("LOO_WI")))
}
```

`r if ('WY' %in% args$states) '### Wyoming'`

#### Effective sample size
Listed below are the parameters with an effective sample size smaller than 500.

```{r, include=('WY' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_WY"))){
  neff <- readRDS(file.to.table("eff_sample_size_cum_WY"))
  neff[which(neff<500)]
}
```

#### Number of divergence and treedepth

```{r, include=('WY' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("diagnostics_WY"))){
  tmp <- readRDS(file.to.table("diagnostics_WY"))
  matrix(c('divergences', 'treedepth', tmp[[1]], tmp[[2]]), nrow = 2, ncol = 2, byrow = T)
}
```

#### WAIC
```{r, include=('WY' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("WAIC_WY"))){
  print(readRDS(file.to.table("WAIC_WY")))
}
```

#### LOO
```{r, include=('WY' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("LOO_WY"))){
  print(readRDS(file.to.table("LOO_WY")))
}
```







## Mean age of deceased individuals over time

```{r, out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("MeanAgeDeath"))){
  knitr::include_graphics(file.to.figure("MeanAgeDeath"))
}
```

